---
title: "runoff_volumes"
output: html_document
---

```{r}
library(tidyverse)
library(here)
```

Source your storm_runoff.R script so you are able to use the predict_runoff function in your .Rmd
```{r}
source(here::here("src", "storm_runoff.R"))
```

Estimate stormwater volume for a watershed of 182 acres, over a range of estimates for the impervious fraction (from 0.6 to 0.8, by increments of 0.01). 
```{r}
Ia_seq = seq(from = 0.6, to = 0.8, by = 0.01)

runoff_volume <- predict_runoff(Ia = Ia_seq, A = 182)
```

Bind your sequence of impervious fractions together with the resulting runoff volume calculated into a data frame. 
```{r}
proj_df <- data.frame(Ia_seq, runoff_volume)

proj_df
```

Create a ggplot graph that has both dots and connecting lines (i.e., you’ll layer geom_point() and geom_line(). Update axis labels. Export a png of your graph to the figs folder using ggsave.

```{r}
ggplot(data = proj_df, aes(x = Ia_seq, y = runoff_volume)) + 
  geom_point(aes(fill = "red"), size = 1, alpha = 0.4, show.legend = FALSE) +
  geom_line(aes(colour = "black"), size = 1, alpha = 1, show.legend = FALSE) + 
  theme_gray() + 
  labs(title = "Range of impervious fraction vs stormwater runoff volume of a watershed",
       x = "Impervious fraction",
       y = "Runoff volume (ft^3)")

ggsave(here::here("figs", "impervious_runoff.png"), height = 5, width = 6)
```

